Posterior summarisation in Bayesian phylogenetics using Tracer 1.7

### 2018-02-02 manuscript/tracer17.tex
last edits to fit onto 3 pages - please check text

Other packages are available for the post-processing of MCMC samples and are largely complementary to \tracer\ .
The R package `coda' \citep{plummer2006coda} provides some of the functionality of \tracer\ within the R programming environment. `AWTY' \citep{nylander2007awty} explores the convergence of the phylogenetic tree parameter itself across multiple MCMC runs.
%% AR - anything else? The MDS tree-space approaches of Hillis etc.?

\vspace{-0.25cm}

@@

\vspace{-0.25cm}

>>>>

%Other packages for post-processing of MCMC samples are

Other packages are available for the post-processing of MCMC samples. % and are largely complementary to \tracer\ .
 `Coda' \citep{plummer2006coda} provides some of the functionality of \tracer\ within the R programming environment, while `AWTY' \citep{nylander2007awty} explores the convergence of the phylogenetic tree parameter itself across multiple MCMC runs.
%% AR - anything else? The MDS tree-space approaches of Hillis etc.?

\vspace{-0.35cm}

@@

\vspace{-0.35cm}
